\section{Feasibility experiments}
\label{sec:feasibility}
To gauge the feasibility of the proposed graduation project several aspects of the Lightyear 0 were researched and some experiments with tools were performed. This section describes how the research and experiments were performed and the resulting models, descriptions and data of the experiments.

Section~\ref{sec:invehicle} describes the architecture of the Lightyear 0's in-vehicle network, explaining the different types of nodes found in the network, which networks the vehicle has and the connections between component and network. The results were created by both talking to experts on the in-vehicle network, reading documentation and reading code that is deployed on the nodes or used to build the binaries. 
Section~\ref{sec:networktraffic} is an investigation into the data that is generated and consumed by the nodes in the network. The goal is to understand what kinds of dataflows exist in the Lightyear 0 so that the network traffic produced by these flows can be modelled accurately during the graduation project. The execution model of the node types mentioned in Section~\ref{sec:invehicle} is described as well to make the dataflow model more accurate. Some scripts have been developed to partially retrieve and generate overviews of the dataflow from the program code. This section is a result of inspecting the build-system and the code that is deployed on the network nodes, followed by a review by the architects and lead software developers of the system.

Lastly in Section~\ref{sec:omnetpp} two experiments performed with the Discrete Event Simulator Omnet++ are explained. The first experiment is a re-implementation of an exercise performed during the \textit{Quantitative Evaluation of Embedded Systems} course which was originally executed in Matlab. The goal is to learn the basics of the simulation framework and validate its ability to perform experiments involving random processes. The second experiment sketches a model of periodic dataflow between software components as found in the Lightyear 0.

\input{6.1.in_vehicle_network.tex}
\clearpage
\input{6.2.network_traffic.tex}
\clearpage
\input{6.3.omnetpp.tex}

\newpage